---
title: "Untitled"
format: html
---

```{r}
library(ggplot2)
library(tidyverse)
```

Define double logistic functions.
```{r}

double_logis7 <- function(d, theta){
  # double logistic function.
  # theta1 is transformed using the logistic function.
  # theta2 is transformed using the 
  # theta4 is transformed using the 
  # theta6 is transformed using the 
  # This allows for all parameters to follow a gaussian distribution
  
  theta[1] <- plogis(theta[1])
  theta[2] <- exp(theta[2])
  theta[4] <- exp(theta[4])
  theta[6] <- exp(theta[6])
  theta[7] <- theta[7]/(1e4)
  
  d1 <- 1 + exp((theta[3] - d)/theta[4])
  
  d2 <- 1 + exp((theta[5] - d)/theta[6])
  
  out <- theta[1] + (theta[2] + (theta[3] + (theta[5] - theta[3])/2  - d)*theta[7] - theta[1])*(1/d1 - 1/d2)
  
  
  return(out)
}

double_logis6 <- function(d, theta){
  # double logistic function.
  # theta1 is transformed using the logistic function.
  # theta2 is transformed using the 
  # theta4 is transformed using the 
  # theta6 is transformed using the 
  # This allows for all parameters to follow a gaussian distribution
  
  theta[1] <- plogis(theta[1])
  theta[2] <- exp(theta[2])
  theta[4] <- exp(theta[4])
  theta[6] <- exp(theta[6])
  
  d1 <- 1 + exp((theta[3] - d)/theta[4])
  
  d2 <- 1 + exp((theta[5] - d)/theta[6])
  
  out <- theta[1] + (theta[2] - theta[1])*(1/d1 - 1/d2)

  
  return(out)
}

```

```{r}

text.size <- 10

theta <- c(-1.7, -0.1, 100, 2.2, 265, 2.8, 5)

ggplot() +
  geom_line(aes(x = 1:366, y = double_logis7(1:366, theta)), color = "red", linewidth = 1) +
  geom_hline(aes(yintercept = plogis(theta[1])), linetype = "dashed") +
  geom_hline(aes(yintercept = exp(theta[2])), linetype = "dashed") +
  geom_vline(aes(xintercept = c(theta[3], theta[5])), linetype = "dashed") +
  geom_abline(aes(intercept = exp(theta[2]) + (theta[7])/1e4*165, slope = -(theta[7])/1e4), linetype = "dashed") +
  geom_errorbarh(aes(xmin = 85, xmax = 115, y = double_logis7(theta[3], theta), height = 0.075), linetype = "dashed") + 
  geom_errorbarh(aes(xmin = 240, xmax = 290, y = double_logis7(theta[5], theta), height = 0.075), linetype = "dashed") + 
  annotate("text", x = 10,            y = plogis(theta[1]) + 0.05,        label = bquote(f(theta[1])), size = text.size/.pt) +
  annotate("text", x = 10,            y = exp(theta[2]) - 0.05,        label = bquote(g(theta[2])), size = text.size/.pt) +
  annotate("text", x = theta[3] + 12, y = 0.04,                              label = bquote(theta[3]), size = text.size/.pt) +
  annotate("text", x = theta[5] + 12, y = 0.04,                              label = bquote(theta[5]), size = text.size/.pt) +
  annotate("text", x = theta[3] + 37, y = double_logis7(theta[3], theta), label = bquote(g(theta[4])), size = text.size/.pt) +
  annotate("text", x = theta[5] + 47, y = double_logis7(theta[5], theta), label = bquote(g(theta[6])), size = text.size/.pt) +
  annotate("text", x = 320, y = exp(theta[2]) - 320*theta[7]/1e4 + 0.03, label = bquote((theta[7]/c)*(d)), size = text.size/.pt, angle = -7.2) +
  scale_y_continuous(limits = c(0,1)) +
  theme_bw(base_size = text.size) +
  ylab("VI") +
  xlab("Day of year, d")

ggsave("/Users/matthewshisler/Spatial BLSP - 20 May 2024/paper_visualization/double_logistic demo/double_logistic7_demo_reparam.pdf", device = "pdf", width = 5.5, height = 3)

```







Make 7-parameter doublelogistic function plot. 16 pt font.
```{r}

text.size <- 16

theta <- c(-1.7, -0.1, 100, 2.2, 265, 2.8, 5)

ggplot() +
  geom_line(aes(x = 1:366, y = double_logis7(1:366, theta)), color = "red", linewidth = 1) +
  geom_hline(aes(yintercept = plogis(theta[1])), linetype = "dashed") +
  geom_vline(aes(xintercept = c(theta[3], theta[5])), linetype = "dashed") +
  geom_abline(aes(intercept = exp(theta[2]), slope = -(theta[7])/1e4), linetype = "dashed") +
  geom_errorbarh(aes(xmin = 85, xmax = 115, y = double_logis7(theta[3], theta), height = 0.075), linetype = "dashed") + 
  geom_errorbarh(aes(xmin = 240, xmax = 290, y = double_logis7(theta[5], theta), height = 0.075), linetype = "dashed") + 
  annotate("text", x = 10,            y = plogis(theta[1]) + 0.05,        label = bquote(g(theta[1])), size = text.size/.pt) +
  annotate("text", x = theta[3] + 12, y = 0.04,                              label = bquote(theta[3]), size = text.size/.pt) +
  annotate("text", x = theta[5] + 12, y = 0.04,                              label = bquote(theta[5]), size = text.size/.pt) +
  annotate("text", x = theta[3] + 37, y = double_logis7(theta[3], theta), label = bquote(h(theta[4])), size = text.size/.pt) +
  annotate("text", x = theta[5] + 47, y = double_logis7(theta[5], theta), label = bquote(h(theta[6])), size = text.size/.pt) +
  annotate("text", x = 180, y = exp(theta[2]) - 180*theta[7]/1e4 + 0.05, label = bquote(h(theta[2]) - (theta[7]/c)*(d)), size = text.size/.pt, angle = -7.2) +
  scale_y_continuous(limits = c(0,1)) +
  theme_bw(base_size = text.size) +
  ylab("VI") +
  xlab("d")

# ggsave("/Users/matthewshisler/Desktop/Bayesian_LSP_April_21/paper_visualization/double_logistic7_demo.pdf", device = "pdf", width = 7, height = 5)
```

Make 6-parameter double-logistic function plot. 16 point font.

```{r}

text.size <- 16

theta <- c(-1.7, -0.1, 100, 2.2, 265, 2.8)

ggplot() +
  geom_line(aes(x = 1:366, y = double_logis6(1:366, theta)), color = "red", linewidth = 1) +
  geom_hline(aes(yintercept = plogis(theta[1])), linetype = "dashed") +
  geom_vline(aes(xintercept = c(theta[3], theta[5])), linetype = "dashed") +
  geom_hline(aes(yintercept = exp(theta[2])), linetype = "dashed") +
  geom_errorbarh(aes(xmin = 85, xmax = 115, y = double_logis6(theta[3], theta), height = 0.075), linetype = "dashed") + 
  geom_errorbarh(aes(xmin = 240, xmax = 290, y = double_logis6(theta[5], theta), height = 0.075), linetype = "dashed") + 
  annotate("text", x = 10,            y = plogis(theta[1]) + 0.05,        label = bquote(g(theta[1])), size = text.size/.pt) +
  annotate("text", x = theta[3] + 12, y = 0.04,                              label = bquote(theta[3]), size = text.size/.pt) +
  annotate("text", x = theta[5] + 12, y = 0.04,                              label = bquote(theta[5]), size = text.size/.pt) +
  annotate("text", x = theta[3] + 37, y = double_logis6(theta[3], theta), label = bquote(h(theta[4])), size = text.size/.pt) +
  annotate("text", x = theta[5] + 47, y = double_logis6(theta[5], theta), label = bquote(h(theta[6])), size = text.size/.pt) +
  annotate("text", x = 180, y = exp(theta[2]) + 0.05, label = bquote(h(theta[2])), size = text.size/.pt) +
  scale_y_continuous(limits = c(0,1)) +
  theme_bw(base_size = text.size) +
  ylab("VI") +
  xlab("d")

# ggsave("/Users/matthewshisler/Desktop/Bayesian_LSP_April_21/paper_visualization/double_logistic6_demo.pdf", device = "pdf", width = 7, height = 5)
```


Make 7-parameter doublelogistic function plot. 20 pt font.
```{r}

text.size <- 20

theta <- c(-1.7, -0.1, 100, 2.2, 265, 2.8, 5)

ggplot() +
  geom_line(aes(x = 1:366, y = double_logis7(1:366, theta)), color = "red", linewidth = 1) +
  geom_hline(aes(yintercept = plogis(theta[1])), linetype = "dashed") +
  geom_vline(aes(xintercept = c(theta[3], theta[5])), linetype = "dashed") +
  geom_abline(aes(intercept = exp(theta[2]), slope = -(theta[7])/1e4), linetype = "dashed") +
  geom_errorbarh(aes(xmin = 85, xmax = 115, y = double_logis7(theta[3], theta), height = 0.075), linetype = "dashed") + 
  geom_errorbarh(aes(xmin = 240, xmax = 290, y = double_logis7(theta[5], theta), height = 0.075), linetype = "dashed") + 
  annotate("text", x = 10,            y = plogis(theta[1]) + 0.075,        label = bquote(g(theta[1])), size = text.size/.pt) +
  annotate("text", x = theta[3] + 12, y = 0.04,                              label = bquote(theta[3]), size = text.size/.pt) +
  annotate("text", x = theta[5] + 12, y = 0.04,                              label = bquote(theta[5]), size = text.size/.pt) +
  annotate("text", x = theta[3] + 40, y = double_logis7(theta[3], theta), label = bquote(h(theta[4])), size = text.size/.pt) +
  annotate("text", x = theta[5] + 50, y = double_logis7(theta[5], theta), label = bquote(h(theta[6])), size = text.size/.pt) +
  annotate("text", x = 180, y = exp(theta[2]) - 180*theta[7]/1e4 + 0.075, label = bquote(h(theta[2]) - (theta[7]/c)*(d)), size = text.size/.pt, angle = -7.1) +
  scale_y_continuous(limits = c(0,1)) +
  theme_bw(base_size = text.size) +
  ylab("VI") +
  xlab("d")

# ggsave("/Users/matthewshisler/Desktop/Bayesian_LSP_April_21/paper_visualization/double_logistic7_demo_20pt.pdf", device = "pdf", width = 7, height = 5)
```

Make 6-parameter double-logistic function plot. 20 point font.

```{r}

text.size <- 20

theta <- c(-1.7, -0.1, 100, 2.2, 265, 2.8)

ggplot() +
  geom_line(aes(x = 1:366, y = double_logis6(1:366, theta)), color = "red", linewidth = 1) +
  geom_hline(aes(yintercept = plogis(theta[1])), linetype = "dashed") +
  geom_vline(aes(xintercept = c(theta[3], theta[5])), linetype = "dashed") +
  geom_hline(aes(yintercept = exp(theta[2])), linetype = "dashed") +
  geom_errorbarh(aes(xmin = 85, xmax = 115, y = double_logis6(theta[3], theta), height = 0.075), linetype = "dashed") + 
  geom_errorbarh(aes(xmin = 240, xmax = 290, y = double_logis6(theta[5], theta), height = 0.075), linetype = "dashed") + 
  annotate("text", x = 10,            y = plogis(theta[1]) + 0.075,        label = bquote(g(theta[1])), size = text.size/.pt) +
  annotate("text", x = theta[3] + 12, y = 0.04,                              label = bquote(theta[3]), size = text.size/.pt) +
  annotate("text", x = theta[5] + 12, y = 0.04,                              label = bquote(theta[5]), size = text.size/.pt) +
  annotate("text", x = theta[3] + 40, y = double_logis6(theta[3], theta), label = bquote(h(theta[4])), size = text.size/.pt) +
  annotate("text", x = theta[5] + 50, y = double_logis6(theta[5], theta), label = bquote(h(theta[6])), size = text.size/.pt) +
  annotate("text", x = 180, y = exp(theta[2]) + 0.075, label = bquote(h(theta[2])), size = text.size/.pt) +
  scale_y_continuous(limits = c(0,1)) +
  theme_bw(base_size = text.size) +
  ylab("VI") +
  xlab("d")

# ggsave("/Users/matthewshisler/Desktop/Bayesian_LSP_April_21/paper_visualization/double_logistic6_demo_20pt.pdf", device = "pdf", width = 7, height = 5)
```


New double-logistic function.
```{r}
double_logis7 <- function(d, theta){
  # double logistic function.
  # theta1 is transformed using the logistic function.
  # theta2 is transformed using the 
  # theta4 is transformed using the 
  # theta6 is transformed using the 
  # This allows for all parameters to follow a gaussian distribution
  
  theta[1] <- plogis(theta[1])
  theta[2] <- exp(theta[2])
  theta[4] <- exp(theta[4])
  theta[6] <- exp(theta[6])
  theta[7] <- theta[7]/(1e4)
  
  d1 <- 1 + exp((theta[3] - d)/theta[4])
  
  d2 <- 1 + exp((theta[5] - d)/theta[6])
  
  out <- theta[1] + (theta[2] + (theta[3] + (theta[5] - theta[3])/2  - d)*theta[7] - theta[1])*(1/d1 - 1/d2)
  
  
  return(out)
}

```

Make 7-parameter doublelogistic function plot. 16 pt font. New parameterization
```{r}

text.size <- 16

theta <- c(-1.7, -0.1, 100, 2.2, 265, 2.8, 5)

ggplot() +
  geom_line(aes(x = 1:366, y = double_logis7(1:366, theta)), color = "red", linewidth = 1) +
  geom_hline(aes(yintercept = plogis(theta[1])), linetype = "dashed") +
  geom_hline(aes(yintercept = exp(theta[2])), linetype = "dashed") +
  geom_vline(aes(xintercept = c(theta[3], theta[5])), linetype = "dashed") +
  geom_abline(aes(intercept = exp(theta[2]) + (theta[7])/1e4*165, slope = -(theta[7])/1e4), linetype = "dashed") +
  geom_errorbarh(aes(xmin = 85, xmax = 115, y = double_logis7(theta[3], theta), height = 0.075), linetype = "dashed") + 
  geom_errorbarh(aes(xmin = 240, xmax = 290, y = double_logis7(theta[5], theta), height = 0.075), linetype = "dashed") + 
  annotate("text", x = 10,            y = plogis(theta[1]) + 0.05,        label = bquote(f(theta[1])), size = text.size/.pt) +
  annotate("text", x = 10,            y = exp(theta[2]) - 0.05,        label = bquote(g(theta[2])), size = text.size/.pt) +
  annotate("text", x = theta[3] + 12, y = 0.04,                              label = bquote(theta[3]), size = text.size/.pt) +
  annotate("text", x = theta[5] + 12, y = 0.04,                              label = bquote(theta[5]), size = text.size/.pt) +
  annotate("text", x = theta[3] + 37, y = double_logis7(theta[3], theta), label = bquote(g(theta[4])), size = text.size/.pt) +
  annotate("text", x = theta[5] + 47, y = double_logis7(theta[5], theta), label = bquote(g(theta[6])), size = text.size/.pt) +
  annotate("text", x = 320, y = exp(theta[2]) - 320*theta[7]/1e4 + 0.03, label = bquote((theta[7]/c)*(d)), size = text.size/.pt, angle = -7.2) +
  scale_y_continuous(limits = c(0,1)) +
  theme_bw(base_size = text.size) +
  ylab("VI") +
  xlab("Day of year, d")

ggsave("/Users/matthewshisler/Spatial BLSP - 20 May 2024/paper_visualization/double_logistic demo/double_logistic7_demo_reparam.pdf", device = "pdf", width = 7, height = 5)
```